A systematic measurement on starspot contrast from TESS and K2 bandpass differences

### 2022-07-29 papers/paper1/ms.tex
Add figures of contrast versus Teff ratio

\documentclass[modern]{aastex631}
\bibliographystyle{aasjournal}

@@

\begin{deluxetable}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition\\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...927..219C} & - & Using deep learning to recover TESS light curves \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\  
  \enddata
\end{deluxetable}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[scale=0.5]{Amplitude Comparison Mask.png}
  \caption{The mask showing how we determined which points to keep and which ones were outliers.}
\end{figure}
\FloatBarrier

@@

\begin{figure}[hbt!]
  \includegraphics[width=0.95\textwidth]{figures/contrast_spectrum2.pdf}
  \caption{Illustration of starspot contrast as seen in \tess\ and \kepler. The red shaded spectrum illustrates the contrast for an M0V spectral type for a choice of spot and ambient photospheric temperatures. The thick blue left-most curve illustrates the \kepler\ passband, the thick green line to its right illustrates the \tess\ passband centered near 850 nm.  A lower number means darker spots.  }
  \label{fig:filtercurve}
\end{figure}

Figure \ref{fig:filtercurve} shows an illustration of wavelength dependent spot contrast for a hypothetical M0V star with $T_\mathrm{phot}=3800\;$K, and with $T_\mathrm{spot}=3300\;$K.  We employ \texttt{PHOENIX} synthetic spectral models \cite{2013A&A...553A...6H}, accessed at these temperatures.  The contrast ascends from near 0.01 at $\lambda=500\;$nm, to 0.15 at 1 $\mu$m.  By 2.3 $\mu$m, the contrast has peaked at 0.3.  The overlapping \kepler\ and \tess\ system throughputs overplotted on Figure \ref{fig:filtercurve} indicate that---on average---the starspot contrast is a lower number in the \kepler passband ($\lambda \sim 550\;$nm)  than for the redder \tess passband ($\lambda \sim 850\;$nm).  Starspots look blacker in \kepler\ and \ktwo\ than they do in \tess.  The understanding of wavelength dependent starspot contrast is not novel--- it has driven the design of precision radial velocity (PRV) spectrographs to the near-IR, where the deleterious effect of starspots on RV jitter is lessened.  The key innovation of this proposal stems from the vast number of sources with existing \ktwo\ data that \tess\ will observe in Cycle 4.  This proposal aims to quantify precisely the starspot contrast differences between the \tess\ and \kepler\ wavelength bands.  We re-iterate that the extent to which nature produces starspot spectra resembling the prescription in Figure \ref{fig:filtercurve} remains an unknown, and is the main thrust of the proposed work effort.

System-throughput-weighted contrast spectra can be integrated over the illustrated filter curves to yield precision estimates for contrasts in the two passbands. For this M0V example, we obtain $c_{\ktwo}\sim0.025$ and $c_{\tess}\sim0.1$. Starspots appear about four times darker in \kepler\ and \ktwo\ than they do in \tess. We define the ratio of starspot contrasts of \tess\ compared to \kepler\ as $\mathcal{R}\equiv \frac{c_{\tess}}{c_{\ktwo}}$. This proposal will systematically measure $\mathcal{R}$ for a vast number of stars observed by both missions.

@@

The notation is cumbersome, but the takeaway is clear: we can quantify spot contrast ratio knowing only the amplitudes of \ktwo\ and \tess\ spot-modulated lightcurves. This equation is approximate, and in practice our team will derive $\mathcal{R}= \frac{c_{\tess}}{c_{\ktwo}}$ with Monte Carlo methods to take into account the uncertainty of the amplitude determination and subtle starspot self-dilution effects.
\newline

@@

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[scale=0.42]{Amplitude vs. Rotation for Kepler and TESS.png}
  \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 3.98\% and 6.94\%, respectively.}
\end{figure}
\FloatBarrier

>>>>

\documentclass[twocolumn]{aastex631}
\bibliographystyle{aasjournal}

@@

\begin{deluxetable*}{chc}
  \tablecaption{Annotated bibliography for intro\label{table1}}
  \tablehead{
    \colhead{Reference} & \nocolhead{two} & \colhead{Key idea}
  }
  \startdata
  \citet{gullysantiago17} & - & LkCa~4 starspot spectral decomposition\\
  \citet{2015ApJ...807..174S} & - & Radius inflation from spots \\
  Strassmeier & - & Starspots review \\
  \citet{2018ApJ...853..122R} & - & TLSE \\
  \citet{Kochukhov21} & - & Magnetic fields of M dwarfs \\
  \citet{2021sf2a.conf..363B} & - & Stellar rotation using ROOSTER \\
  \citet{2015MNRAS.450.3211A} & - & Using Kepler to study stellar rotation \\
  \citet{2022ApJ...927..219C} & - & Using deep learning to recover TESS light curves \\
  \citet{2021AJ....162..123L} & - & Test Lightcurve and study stellar surfaces \\
  \citet{2022ApJ...925..185D} & - & Lightcurves for oblate, rapid rotators \\
  \citet{Reinhold2013} & - & Measure rotation of active Kepler Stars \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\
  % \citet{} & - & \\  
  \enddata
\end{deluxetable*}

@@

\begin{figure*}[!htb]
  \centering
  \includegraphics[scale=0.5]{Amplitude Comparison Mask.png}
  \caption{The mask showing how we determined which points to keep and which ones were outliers.}
\end{figure*}
\FloatBarrier

@@

\begin{figure*}[hbt!]
  \includegraphics[width=0.95\textwidth]{figures/contrast_spectrum2.pdf}
  \caption{Illustration of starspot contrast as seen in \tess\ and \kepler. The red shaded spectrum illustrates the contrast for an M0V spectral type for a choice of spot and ambient photospheric temperatures. The thick blue left-most curve illustrates the \kepler\ passband, the thick green line to its right illustrates the \tess\ passband centered near 850 nm.  A lower number means darker spots.  }
  \label{fig:filtercurve}
\end{figure*}

Figure \ref{fig:filtercurve} shows an illustration of wavelength dependent spot contrast for a hypothetical K star with $T_\mathrm{phot}=4500\;$K, and with $T_\mathrm{spot}=2700\;$K.  We employ \texttt{PHOENIX} synthetic spectral models \cite{2013A&A...553A...6H}, accessed at these temperatures.  The contrast ascends from near 0.01 at $\lambda=500\;$nm, to 0.15 at 1 $\mu$m.  By 2.3 $\mu$m, the contrast has peaked at 0.3.  The overlapping \kepler\ and \tess\ system throughputs overplotted on Figure \ref{fig:filtercurve} indicate that---on average---the starspot contrast is a lower number in the \kepler passband ($\lambda \sim 550\;$nm)  than for the redder \tess passband ($\lambda \sim 850\;$nm).  Starspots look blacker in \kepler\ and \ktwo\ than they do in \tess.  The understanding of wavelength dependent starspot contrast is not novel--- it has driven the design of precision radial velocity (PRV) spectrographs to the near-IR, where the deleterious effect of starspots on RV jitter is lessened.  The key innovation of this proposal stems from the vast number of sources with existing \ktwo\ data that \tess\ will observe in Cycle 4.  This proposal aims to quantify precisely the starspot contrast differences between the \tess\ and \kepler\ wavelength bands.  We re-iterate that the extent to which nature produces starspot spectra resembling the prescription in Figure \ref{fig:filtercurve} remains an unknown, and is the main thrust of the proposed work effort.

System-throughput-weighted contrast spectra can be integrated over the illustrated filter curves to yield precision estimates for contrasts in the two passbands. For this M0V example, we obtain $c_{\ktwo}\sim0.025$ and $c_{\tess}\sim0.1$. Starspots appear about four times darker in \kepler\ and \ktwo\ than they do in \tess. We define the ratio of starspot contrasts of \tess\ compared to \kepler\ as $\mathcal{R}\equiv \frac{c_{\tess}}{c_{\ktwo}}$.

@@

For our example with a 4500 K ambient photosphere and 2700 K starspot characteristic temperature, we obtained $c_{\ktwo}\sim0.025$ and $c_{\tess}\sim0.1$, yielding an expected amplitude ratio of:

$$\frac{1-c_{TESS}}{1-c_{Kepler}} = \frac{1-0.1}{1-0.025}  = (0.9/0.975)=0.923$$

\authorcomment1{We are not currently weighting by the TESS and K2 filter curves.  Here are the values we get when we take the mean:}

$$\frac{1-c_{TESS}}{1-c_{Kepler}} = \frac{1-0.104}{1-0.00697}  = (0.896/0.99303)=0.902$$

% TESS - 0.104
% Kepler - 0.00697

This equation is approximate, and in practice our team will derive $\mathcal{R}= \frac{c_{\tess}}{c_{\ktwo}}$ with Monte Carlo methods to take into account the uncertainty of the amplitude determination and subtle starspot self-dilution effects.
\newline

@@

\subsection{Starspot contrast theory}
Tbd...

\begin{figure}
  \gridline{\fig{figures/Kepler_contrast.png}{0.3\textwidth}{(a)}}
  \gridline{\fig{figures/TESS_contrast.png}{0.3\textwidth}{(b)}}
  \gridline{\fig{one_minus_ratio.png}{0.3\textwidth}{(c)}}
  \caption{A nice inverted pyramid figure
    consisting of six individual files}
\end{figure}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.95\columnwidth]{Amplitude vs. Rotation for Kepler and TESS.png}
  \caption{Effect size for starspot contrast as seen in modulation amplitude versus period ($P_{\mathrm{rot}}$ [days]). The black points are the locus of spotted stars in the Kepler as measured by for late K dwarfs. The red points are the same stars, but measured with the TESS mission. The blue and green dashed lines represents the average amplitudes for all plotted stars for both Kepler and TESS, approximately 3.98\% and 6.94\%, respectively.}
\end{figure}
\FloatBarrier
